A Road Segment Prioritization Approach for Cycling Infrastructure

### 2022-09-14 paper-original-submission.tex
edit response doc

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=2cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage{float}
\usepackage{multirow}
\usepackage{placeins}
\usepackage{multicol}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A Road Segment Prioritization Approach for Cycling Infrastructure},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{A Road Segment Prioritization Approach for Cycling Infrastructure}
\author{}
\date{\vspace{-2.5em}}

@@

@@

Our work builds on these \emph{community finding} approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
within communities. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose an approach that
accounts for motivators and deterrents to cycling. We propose three
sub-methods that address some of the limitations of previous
studies. These limitations include (a) an inherent bias of basing network
design solely on existing cycling demand, (b) the proposal of routes that may
not correspond to studies on cyclist preference and government policies,
and (c) an insufficient consideration of the ethical principles underlying
the analysis. The current work addresses these limitations through the following organisation. Section \ref{calculating-potential-cycling-demand}
focuses on calculating potential cycling demand. Section \ref{routing}
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\ref{road-segment-prioritization} outlines a method for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
`egalitarianism' to one grounded in `utilitarianism'.

@@

\noindent where \(d\) and \(s\) are the distance and slope associated with each
OD pair, and \(\alpha\) and all \(\beta\)s, are parameters calculated by a regression
model on the training data. The square and square-root distance terms
``capture the non-linear impact of distance on the likelihood of
cycling'', and interaction terms to capture the combined effect of slope
and distance (Lovelace et al., 2017). Alternative cycling uptake
models could be `plugged in' to our approach for different contexts or scenarios of change.

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-akbarzadeh2018designing}{}}%
Akbarzadeh, M., Mohri, S.S., Yazdian, E., 2018. Designing bike networks using the concept of network clusters. Applied network science 3, 12.

\leavevmode\vadjust pre{\hypertarget{ref-aldred2019impacts}{}}%
Aldred, R., Croft, J., Goodman, A., 2019. Impacts of an active travel intervention with a cycling focus in a suburban context: One-year findings from an evaluation of london's in-progress mini-hollands programme. Transportation research part A: policy and practice 123, 147--169.

\leavevmode\vadjust pre{\hypertarget{ref-bao2017planning}{}}%
Bao, J., He, T., Ruan, S., Li, Y., Zheng, Y., 2017. Planning bike lanes based on sharing-bikes' trajectories, in: Proceedings of the 23rd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. pp. 1377--1386.

\leavevmode\vadjust pre{\hypertarget{ref-black1995spatial}{}}%
Black, W.R., 1995. Spatial interaction modeling using artificial neural networks. Journal of Transport Geography 3, 159--166.

\leavevmode\vadjust pre{\hypertarget{ref-blondel2008fast}{}}%
Blondel, V.D., Guillaume, J.-L., Lambiotte, R., Lefebvre, E., 2008. Fast unfolding of communities in large networks. Journal of statistical mechanics: theory and experiment 2008, P10008.

\leavevmode\vadjust pre{\hypertarget{ref-brand_climate_2020}{}}%
Brand, C., Dons, E., Anaya-Boig, E., Avila-Palencia, I., Clark, A., de Nazelle, A., Gascon, M., Gaupp-Berghausen, M., Gerike, R., Gotschi, T., 2020. The climate change mitigation effects of active travel. Preprint: researchsquare.com.

\leavevmode\vadjust pre{\hypertarget{ref-broach2011bicycle}{}}%
Broach, J., Gliebe, J., Dill, J., 2011. Bicycle route choice model developed using revealed preference GPS data, in: 90th Annual Meeting of the Transportation Research Board, Washington, DC.

\leavevmode\vadjust pre{\hypertarget{ref-caulfield2012determining}{}}%
Caulfield, B., Brick, E., McCarthy, O.T., 2012. Determining bicycle infrastructure preferences--a case study of dublin. Transportation research part D: transport and environment 17, 413--417.

\leavevmode\vadjust pre{\hypertarget{ref-celis2017association}{}}%
Celis-Morales, C.A., Lyall, D.M., Welsh, P., Anderson, J., Steell, L., Guo, Y., Maldonado, R., Mackay, D.F., Pell, J.P., Sattar, N., others, 2017. Association between active commuting and incident cardiovascular disease, cancer, and mortality: Prospective cohort study. bmj 357, j1456.

\leavevmode\vadjust pre{\hypertarget{ref-crane2017longitudinal}{}}%
Crane, M., Rissel, C., Standen, C., Ellison, A., Ellison, R., Wen, L.M., Greaves, S., 2017. Longitudinal evaluation of travel and health outcomes in relation to new bicycle infrastructure, sydney, australia. Journal of Transport \& Health 6, 386--395.

\leavevmode\vadjust pre{\hypertarget{ref-departmentgearchange2020}{}}%
DfT, 2020a. Gear change: A bold vision for cycling and walking.

\leavevmode\vadjust pre{\hypertarget{ref-departmentcycleinfradesign2020}{}}%
DfT, 2020b. Cycling infrastructure design.

\leavevmode\vadjust pre{\hypertarget{ref-department2012guidance}{}}%
DfT, 2012. Guidance on road classification and the primary route network.

\leavevmode\vadjust pre{\hypertarget{ref-dill2013four}{}}%
Dill, J., McNeil, N., 2013. Four types of cyclists? Examination of typology for better understanding of bicycling behavior and potential. Transportation Research Record 2387, 129--138.

\leavevmode\vadjust pre{\hypertarget{ref-duthie2014optimization}{}}%
Duthie, J., Unnikrishnan, A., 2014. Optimization framework for bicycle network design. Journal of Transportation engineering 140, 04014028.

\leavevmode\vadjust pre{\hypertarget{ref-furth2016network}{}}%
Furth, P.G., Mekuria, M.C., Nixon, H., 2016. Network connectivity for low-stress bicycling. Transportation research record 2587, 41--49.

\leavevmode\vadjust pre{\hypertarget{ref-gehrke2020cycling}{}}%
Gehrke, S.R., Akhavan, A., Furth, P.G., Wang, Q., Reardon, T.G., 2020. A cycling-focused accessibility tool to support regional bike network connectivity. Transportation research part D: transport and environment 85, 102388.

\leavevmode\vadjust pre{\hypertarget{ref-goodman2019scenarios}{}}%
Goodman, A., Rojas, I.F., Woodcock, J., Aldred, R., Berkoff, N., Morgan, M., Abbas, A., Lovelace, R., 2019. Scenarios of cycling to school in england, and associated health and carbon impacts: Application of the {``propensity to cycle tool.''} Journal of Transport \& Health 12, 263--278.

\leavevmode\vadjust pre{\hypertarget{ref-goodman2014new}{}}%
Goodman, A., Sahlqvist, S., Ogilvie, D., Consortium, iConnect, 2014. New walking and cycling routes and increased physical activity: One-and 2-year findings from the UK iConnect study. American journal of public health 104, e38--e46.

\leavevmode\vadjust pre{\hypertarget{ref-gossling2013urban}{}}%
Gössling, S., 2013. Urban transport transitions: Copenhagen, city of cyclists. Journal of Transport Geography 33, 196--206.

\leavevmode\vadjust pre{\hypertarget{ref-iacono2010measuring}{}}%
Iacono, M., Krizek, K.J., El-Geneidy, A., 2010. Measuring non-motorized accessibility: Issues, alternatives, and execution. Journal of Transport Geography 18, 133--140.

\leavevmode\vadjust pre{\hypertarget{ref-jafino2020transport}{}}%
Jafino, B.A., Kwakkel, J., Verbraeck, A., 2020. Transport network criticality metrics: A comparative analysis and a guideline for selection. Transport Reviews 40, 241--264.

\leavevmode\vadjust pre{\hypertarget{ref-jarrett2012effect}{}}%
Jarrett, J., Woodcock, J., Griffiths, U.K., Chalabi, Z., Edwards, P., Roberts, I., Haines, A., 2012. Effect of increasing active travel in urban england and wales on costs to the national health service. The Lancet 379, 2198--2205.

\leavevmode\vadjust pre{\hypertarget{ref-kohl2012pandemic}{}}%
Kohl 3rd, H.W., Craig, C.L., Lambert, E.V., Inoue, S., Alkandari, J.R., Leetongin, G., Kahlmeier, S., Group, L.P.A.S.W., others, 2012. The pandemic of physical inactivity: Global action for public health. The lancet 380, 294--305.

\leavevmode\vadjust pre{\hypertarget{ref-lovelace2017propensity}{}}%
Lovelace, R., Goodman, A., Aldred, R., Berkoff, N., Abbas, A., Woodcock, J., 2017. The propensity to cycle tool: An open source online system for sustainable transport planning. Journal of transport and land use 10, 505--528.

\leavevmode\vadjust pre{\hypertarget{ref-lucas2016method}{}}%
Lucas, K., Van Wee, B., Maat, K., 2016. A method to evaluate equitable accessibility: Combining ethical theories and accessibility-based approaches. Transportation 43, 473--490.

\leavevmode\vadjust pre{\hypertarget{ref-marques2015infrastructure}{}}%
Marqués, R., Hernández-Herrador, V., Calvo-Salazar, M., García-Cebrián, J., 2015. How infrastructure can promote cycling in cities: Lessons from seville. Research in Transportation Economics 53, 31--44.

\leavevmode\vadjust pre{\hypertarget{ref-martinez2013new}{}}%
Martínez, L.M., Viegas, J.M., 2013. A new approach to modelling distance-decay functions for accessibility assessment in transport studies. Journal of Transport Geography 26, 87--96.

\leavevmode\vadjust pre{\hypertarget{ref-mauttone2017bicycle}{}}%
Mauttone, A., Mercadante, G., Rabaza, M., Toledo, F., 2017. Bicycle network design: Model and solution algorithm. Transportation research procedia 27, 969--976.

\leavevmode\vadjust pre{\hypertarget{ref-mesbah2012bilevel}{}}%
Mesbah, M., Thompson, R., Moridpour, S., 2012. Bilevel optimization approach to design of network of bike lanes. Transportation research record 2284, 21--28.

\leavevmode\vadjust pre{\hypertarget{ref-nahmias2017integrating}{}}%
Nahmias-Biran, B., Martens, K., Shiftan, Y., 2017. Integrating equity in transportation project assessment: A philosophical exploration and its practical implications. Transport reviews 37, 192--210.

\leavevmode\vadjust pre{\hypertarget{ref-nello2020environmental}{}}%
Nello-Deakin, S., 2020. Environmental determinants of cycling: Not seeing the forest for the trees? Journal of transport geography 85, 102704.

\leavevmode\vadjust pre{\hypertarget{ref-olmos2020data}{}}%
Olmos, L.E., Tadeo, M.S., Vlachogiannis, D., Alhasoun, F., Alegre, X.E., Ochoa, C., Targa, F., González, M.C., 2020. A data science framework for planning the growth of bicycle infrastructures. Transportation Research Part C: Emerging Technologies 115, 102640.

\leavevmode\vadjust pre{\hypertarget{ref-ofn2018population}{}}%
ONS, 2018. Population estimates for the UK, england and wales, scotland and northern ireland: Mid-2017. Hampshire: Office for National Statistics.

\leavevmode\vadjust pre{\hypertarget{ref-ONS2011flowdata}{}}%
ONS, 2011. 2011 census: Special workplace statistics (united kingdom).

\leavevmode\vadjust pre{\hypertarget{ref-padgham2019dodgr}{}}%
Padgham, M., 2019. Dodgr: An r package for network flow aggregation. Transport Findings. Network Design Lab.

\leavevmode\vadjust pre{\hypertarget{ref-parkin2018designing}{}}%
Parkin, J., 2018. Designing for cycle traffic. ICE Publishing. \url{https://doi.org/10.1680/dfct.63495}

\leavevmode\vadjust pre{\hypertarget{ref-patterson2020associations}{}}%
Patterson, R., Panter, J., Vamos, E.P., Cummins, S., Millett, C., Laverty, A.A., 2020. Associations between commute mode and cardiovascular disease, cancer, and all-cause mortality, and cancer incidence, using linked census data over 25 years in england and wales: A cohort study. The Lancet Planetary Health 4, e186--e194.

\leavevmode\vadjust pre{\hypertarget{ref-pereira2017distributive}{}}%
Pereira, R.H., Schwanen, T., Banister, D., 2017. Distributive justice and equity in transportation. Transport reviews 37, 170--191.

\leavevmode\vadjust pre{\hypertarget{ref-pucher2008making}{}}%
Pucher, J., Buehler, R., 2008. Making cycling irresistible: Lessons from the netherlands, denmark and germany. Transport reviews 28, 495--528.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={A Road Segment Prioritization Approach for Cycling Infrastructure},
  pdfauthor={Hussein Mahfouz1,; Elsa Arcaute1; Robin Lovelace2},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=2cm]{geometry}
\usepackage{longtable,booktabs}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage{float}
\usepackage{multirow}
\usepackage{placeins}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{array}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{A Road Segment Prioritization Approach for Cycling Infrastructure}
\author{Hussein Mahfouz\textsuperscript{1,*} \and Elsa Arcaute\textsuperscript{1} \and Robin Lovelace\textsuperscript{2}}
\date{}

@@

\textsuperscript{1} Centre for Advanced Spatial Analysis (CASA), University College London, London, UK\\
\textsuperscript{2} Institute of Transport Studies, University of Leeds, Leeds, UK

\textsuperscript{*} Correspondence: \href{mailto:h.mahfouz.19@ucl.ac.uk}{Hussein Mahfouz \textless{}\href{mailto:h.mahfouz.19@ucl.ac.uk}{\nolinkurl{h.mahfouz.19@ucl.ac.uk}}\textgreater{}}

@@

Our work builds on these \emph{community finding} approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
within communities. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose an approach that
accounts for motivators and deterrents to cycling. We propose three
sub-methods that address some of the limitations of previous
studies. These limitations include (a) an inherent bias of basing network
design solely on existing cycling demand, (b) the proposal of routes that may
not correspond to studies on cyclist preference and government policies,
and (c) an insufficient consideration of the ethical principles underlying
the analysis. The current work addresses these limitations through the following organisation. Section \ref{calculating-potential-cycling-demand}
focuses on calculating potential cycling demand. Section \ref{routing}
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\ref{road-segment-prioritization} outlines a method for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
`egalitarianism' to one grounded in `utilitarianism.'

@@

\noindent where \(d\) and \(s\) are the distance and slope associated with each
OD pair, and \(\alpha\) and all \(\beta\)s, are parameters calculated by a regression
model on the training data. The square and square-root distance terms
``capture the non-linear impact of distance on the likelihood of
cycling,'' and interaction terms to capture the combined effect of slope
and distance (Lovelace et al., 2017). Alternative cycling uptake
models could be `plugged in' to our approach for different contexts or scenarios of change.

@@

\begin{verbatim}
## Warning: package 'tidyr' was built under R version 4.0.5
\end{verbatim}

\begin{verbatim}
## Warning: package 'readr' was built under R version 4.0.5
\end{verbatim}

\begin{verbatim}
## Warning: package 'dplyr' was built under R version 4.0.5
\end{verbatim}

\begin{verbatim}
## Warning: package 'sf' was built under R version 4.0.5
\end{verbatim}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-akbarzadeh2018designing}{}%
Akbarzadeh, M., Mohri, S.S., Yazdian, E., 2018. Designing bike networks using the concept of network clusters. Applied network science 3, 12.

\leavevmode\hypertarget{ref-aldred2019impacts}{}%
Aldred, R., Croft, J., Goodman, A., 2019. Impacts of an active travel intervention with a cycling focus in a suburban context: One-year findings from an evaluation of london's in-progress mini-hollands programme. Transportation research part A: policy and practice 123, 147--169.

\leavevmode\hypertarget{ref-bao2017planning}{}%
Bao, J., He, T., Ruan, S., Li, Y., Zheng, Y., 2017. Planning bike lanes based on sharing-bikes' trajectories, in: Proceedings of the 23rd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. pp. 1377--1386.

\leavevmode\hypertarget{ref-black1995spatial}{}%
Black, W.R., 1995. Spatial interaction modeling using artificial neural networks. Journal of Transport Geography 3, 159--166.

\leavevmode\hypertarget{ref-blondel2008fast}{}%
Blondel, V.D., Guillaume, J.-L., Lambiotte, R., Lefebvre, E., 2008. Fast unfolding of communities in large networks. Journal of statistical mechanics: theory and experiment 2008, P10008.

\leavevmode\hypertarget{ref-brand_climate_2020}{}%
Brand, C., Dons, E., Anaya-Boig, E., Avila-Palencia, I., Clark, A., de Nazelle, A., Gascon, M., Gaupp-Berghausen, M., Gerike, R., Gotschi, T., 2020. The climate change mitigation effects of active travel. Preprint: researchsquare.com.

\leavevmode\hypertarget{ref-broach2011bicycle}{}%
Broach, J., Gliebe, J., Dill, J., 2011. Bicycle route choice model developed using revealed preference GPS data, in: 90th Annual Meeting of the Transportation Research Board, Washington, DC.

\leavevmode\hypertarget{ref-caulfield2012determining}{}%
Caulfield, B., Brick, E., McCarthy, O.T., 2012. Determining bicycle infrastructure preferences--a case study of dublin. Transportation research part D: transport and environment 17, 413--417.

\leavevmode\hypertarget{ref-celis2017association}{}%
Celis-Morales, C.A., Lyall, D.M., Welsh, P., Anderson, J., Steell, L., Guo, Y., Maldonado, R., Mackay, D.F., Pell, J.P., Sattar, N., others, 2017. Association between active commuting and incident cardiovascular disease, cancer, and mortality: Prospective cohort study. bmj 357, j1456.

\leavevmode\hypertarget{ref-crane2017longitudinal}{}%
Crane, M., Rissel, C., Standen, C., Ellison, A., Ellison, R., Wen, L.M., Greaves, S., 2017. Longitudinal evaluation of travel and health outcomes in relation to new bicycle infrastructure, sydney, australia. Journal of Transport \& Health 6, 386--395.

\leavevmode\hypertarget{ref-departmentgearchange2020}{}%
DfT, 2020a. Gear change: A bold vision for cycling and walking.

\leavevmode\hypertarget{ref-departmentcycleinfradesign2020}{}%
DfT, 2020b. Cycling infrastructure design.

\leavevmode\hypertarget{ref-department2012guidance}{}%
DfT, 2012. Guidance on road classification and the primary route network.

\leavevmode\hypertarget{ref-dill2013four}{}%
Dill, J., McNeil, N., 2013. Four types of cyclists? Examination of typology for better understanding of bicycling behavior and potential. Transportation Research Record 2387, 129--138.

\leavevmode\hypertarget{ref-duthie2014optimization}{}%
Duthie, J., Unnikrishnan, A., 2014. Optimization framework for bicycle network design. Journal of Transportation engineering 140, 04014028.

\leavevmode\hypertarget{ref-furth2016network}{}%
Furth, P.G., Mekuria, M.C., Nixon, H., 2016. Network connectivity for low-stress bicycling. Transportation research record 2587, 41--49.

\leavevmode\hypertarget{ref-gehrke2020cycling}{}%
Gehrke, S.R., Akhavan, A., Furth, P.G., Wang, Q., Reardon, T.G., 2020. A cycling-focused accessibility tool to support regional bike network connectivity. Transportation research part D: transport and environment 85, 102388.

\leavevmode\hypertarget{ref-goodman2019scenarios}{}%
Goodman, A., Rojas, I.F., Woodcock, J., Aldred, R., Berkoff, N., Morgan, M., Abbas, A., Lovelace, R., 2019. Scenarios of cycling to school in england, and associated health and carbon impacts: Application of the {`propensity to cycle tool.'} Journal of Transport \& Health 12, 263--278.

\leavevmode\hypertarget{ref-goodman2014new}{}%
Goodman, A., Sahlqvist, S., Ogilvie, D., Consortium, iConnect, 2014. New walking and cycling routes and increased physical activity: One-and 2-year findings from the UK iConnect study. American journal of public health 104, e38--e46.

\leavevmode\hypertarget{ref-gossling2013urban}{}%
Gössling, S., 2013. Urban transport transitions: Copenhagen, city of cyclists. Journal of Transport Geography 33, 196--206.

\leavevmode\hypertarget{ref-iacono2010measuring}{}%
Iacono, M., Krizek, K.J., El-Geneidy, A., 2010. Measuring non-motorized accessibility: Issues, alternatives, and execution. Journal of Transport Geography 18, 133--140.

\leavevmode\hypertarget{ref-jafino2020transport}{}%
Jafino, B.A., Kwakkel, J., Verbraeck, A., 2020. Transport network criticality metrics: A comparative analysis and a guideline for selection. Transport Reviews 40, 241--264.

\leavevmode\hypertarget{ref-jarrett2012effect}{}%
Jarrett, J., Woodcock, J., Griffiths, U.K., Chalabi, Z., Edwards, P., Roberts, I., Haines, A., 2012. Effect of increasing active travel in urban england and wales on costs to the national health service. The Lancet 379, 2198--2205.

\leavevmode\hypertarget{ref-kohl2012pandemic}{}%
Kohl 3rd, H.W., Craig, C.L., Lambert, E.V., Inoue, S., Alkandari, J.R., Leetongin, G., Kahlmeier, S., Group, L.P.A.S.W., others, 2012. The pandemic of physical inactivity: Global action for public health. The lancet 380, 294--305.

\leavevmode\hypertarget{ref-lovelace2017propensity}{}%
Lovelace, R., Goodman, A., Aldred, R., Berkoff, N., Abbas, A., Woodcock, J., 2017. The propensity to cycle tool: An open source online system for sustainable transport planning. Journal of transport and land use 10, 505--528.

\leavevmode\hypertarget{ref-lucas2016method}{}%
Lucas, K., Van Wee, B., Maat, K., 2016. A method to evaluate equitable accessibility: Combining ethical theories and accessibility-based approaches. Transportation 43, 473--490.

\leavevmode\hypertarget{ref-marques2015infrastructure}{}%
Marqués, R., Hernández-Herrador, V., Calvo-Salazar, M., García-Cebrián, J., 2015. How infrastructure can promote cycling in cities: Lessons from seville. Research in Transportation Economics 53, 31--44.

\leavevmode\hypertarget{ref-martinez2013new}{}%
Martínez, L.M., Viegas, J.M., 2013. A new approach to modelling distance-decay functions for accessibility assessment in transport studies. Journal of Transport Geography 26, 87--96.

\leavevmode\hypertarget{ref-mauttone2017bicycle}{}%
Mauttone, A., Mercadante, G., Rabaza, M., Toledo, F., 2017. Bicycle network design: Model and solution algorithm. Transportation research procedia 27, 969--976.

\leavevmode\hypertarget{ref-mesbah2012bilevel}{}%
Mesbah, M., Thompson, R., Moridpour, S., 2012. Bilevel optimization approach to design of network of bike lanes. Transportation research record 2284, 21--28.

\leavevmode\hypertarget{ref-nahmias2017integrating}{}%
Nahmias-Biran, B., Martens, K., Shiftan, Y., 2017. Integrating equity in transportation project assessment: A philosophical exploration and its practical implications. Transport reviews 37, 192--210.

\leavevmode\hypertarget{ref-nello2020environmental}{}%
Nello-Deakin, S., 2020. Environmental determinants of cycling: Not seeing the forest for the trees? Journal of transport geography 85, 102704.

\leavevmode\hypertarget{ref-olmos2020data}{}%
Olmos, L.E., Tadeo, M.S., Vlachogiannis, D., Alhasoun, F., Alegre, X.E., Ochoa, C., Targa, F., González, M.C., 2020. A data science framework for planning the growth of bicycle infrastructures. Transportation Research Part C: Emerging Technologies 115, 102640.

\leavevmode\hypertarget{ref-ofn2018population}{}%
ONS, 2018. Population estimates for the UK, england and wales, scotland and northern ireland: Mid-2017. Hampshire: Office for National Statistics.

\leavevmode\hypertarget{ref-ONS2011flowdata}{}%
ONS, 2011. 2011 census: Special workplace statistics (united kingdom).

\leavevmode\hypertarget{ref-padgham2019dodgr}{}%
Padgham, M., 2019. Dodgr: An r package for network flow aggregation. Transport Findings. Network Design Lab.

\leavevmode\hypertarget{ref-parkin2018designing}{}%
Parkin, J., 2018. Designing for cycle traffic. ICE Publishing. \url{https://doi.org/10.1680/dfct.63495}

\leavevmode\hypertarget{ref-patterson2020associations}{}%
Patterson, R., Panter, J., Vamos, E.P., Cummins, S., Millett, C., Laverty, A.A., 2020. Associations between commute mode and cardiovascular disease, cancer, and all-cause mortality, and cancer incidence, using linked census data over 25 years in england and wales: A cohort study. The Lancet Planetary Health 4, e186--e194.

\leavevmode\hypertarget{ref-pereira2017distributive}{}%
Pereira, R.H., Schwanen, T., Banister, D., 2017. Distributive justice and equity in transportation. Transport reviews 37, 170--191.

\leavevmode\hypertarget{ref-pucher2008making}{}%
Pucher, J., Buehler, R., 2008. Making cycling irresistible: Lessons from the netherlands, denmark and germany. Transport reviews 28, 495--528.

\leavevmode\hypertarget{ref-pucher2010infrastructure}{}%
Pucher, J., Dill, J., Handy, S., 2010. Infrastructure, programs, and policies to increase bicycling: An international review. Preventive medicine 50, S106--S125.

\leavevmode\hypertarget{ref-schoner2014missing}{}%
Schoner, J.E., Levinson, D.M., 2014. The missing link: Bicycle infrastructure networks and ridership in 74 US cities. Transportation 41, 1187--1204.

\leavevmode\hypertarget{ref-sorton1994bicycle}{}%
Sorton, A., Walsh, T., 1994. Bicycle stress level as a tool to evaluate urban and suburban bicycle compatibility. Transportation Research Record 17--17.

\leavevmode\hypertarget{ref-stinson2003commuter}{}%
Stinson, M.A., Bhat, C.R., 2003. Commuter bicyclist route choice: Analysis using a stated preference survey. Transportation Research Record 1828, 107--115.

\leavevmode\hypertarget{ref-agreement2015paris}{}%
UN, 2015. Paris agreement, in: Report of the Conference of the Parties to the United Nations Framework Convention on Climate Change (21st Session, 2015: Paris). Retrived December. HeinOnline, p. 2017.
